---
title: "Using Chicken Weigts Study for EDA and Statistics"
author: "Mansour Al-Humaid"
date: "10/17/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, 
                      message = FALSE,
                      warning = FALSE,
                      echo = FALSE,
                      autodep = TRUE, 
                      fig.align = "center")
library(DT)
library(tidyverse)


```

# Analysis of Chicken Weights by Comparing different food supplements effects on the growth rate of chickens

This dataset was derived to study the impact of different food supplements on the growth rate of chickens.


### Exploratory Data Analysis (EDA) & Statistics:

```{r}
knitr::kable(summary(chickwts))
```

#### This data contains 2 variables.

*1. Weight*: Referring to Chicken weight.

*2. Feed*: Referring to Feed type.


```{r output="asis"  ,echo = FALSE}

chickwts %>% 
  group_by(feed) %>%
 summarise(n = n(),
               average = mean(weight),
               SD = sd(weight))
  
```

#### Descriptive Statistics:

```{r}
datatable(chickwts %>%
  group_by(feed) %>%
    summarise(Number_of_observations=length(feed),
              Average_Weight=mean(weight),
              SD=sd(weight)))
```



### Plots and Visulaization:

Below plots gives more insights about food effects on chicken weights



**PLOTS**

```{r, echo=FALSE}
ggplot(chickwts, aes( x = feed, y =  weight )) + 
  geom_boxplot()
```



```{r, echo = FALSE}
ggplot(chickwts,aes(x=feed, y=weight)) + 
  geom_jitter() + 
  stat_summary(fun.data = mean_sdl,
               fun.args = list(mult=1),
               color="blue")
```

measure the impact of food on chicken weight 





```{r}
chickwts_lm <- lm(weight ~ feed , data =  chickwts)
chickwts_lm
anova(chickwts_lm)

```
  
```



```{r}
lm(formula = weight ~ feed, data = chickwts)

```

