---
title: "Case Study of Diamonds Dataset Analysis for EDA and Statistics"
author: "Mansour Al-Humaid"
date: "10/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, 
                      message = FALSE,
                      warning = FALSE,
                      echo = FALSE,
                      autodep = TRUE, 
                      fig.align = "center")
library(DT)
library(tidyverse)
library(rio)
library(ggplot2)

```

# Analysis of Diamonds Dataset using EDA and Descriptive Statistics

### Exploring Data by diamonds cuts with count and average price


```{r}
jems2 <- read_csv("data/diamonds.csv")
datatable(diamonds %>%
  group_by(cut) %>%
    summarise(Count=length(cut),
              Average_Price=mean(price),
             ))

```


Diamonds Dataset Summary
```{r}
summary(diamonds)
```





### How many diamonds with a clarity of category “IF” are present in the data-set?What fraction of the total do they represent?
```{r}
jems2 %>% 
  filter(clarity == "IF") -> clarity_IF

jems2 %>%
  filter(clarity == "IF") %>%
  nrow()

```


### What proportion of the whole is made up of each category of clarity?
```{r}
jems2 %>% 
  group_by(jems2$clarity) %>% 
  mean()
```


### What is the cheapest diamond price? 
```{r}
min(jems2$price)
```


### What is the range of diamond prices?
```{r}
range(jems2$price)
```



### What is the average diamond price in each category of cut and color?
```{r}
jems2 %>% 
  group_by(cut, color) %>% 
  summarise(mean(price))
```



### A scatter plot of the price of a diamond as described by the carat
```{r}
ggplot(jems2, aes(x= carat, y=price)) + 
  geom_point()
```



```{r}

lm(jems2$carat ~ jems2$price, jems2)

price_log10 <- log10(jems2$price)
carat_log10 <- log10(jems2$carat)
```





### A scatter plot of the price of a diamond as described by the carat with log 10 applied
```{r}
ggplot(jems2, aes(x= carat_log10, y=price_log10)) + 
  geom_point()
```



### to recreate a model that describes the relationship shown in the plot?
```{r}
jems2_lm <- lm(price_log10  ~  carat_log10, data= jems2)
jems2_lm
```




### the price of a diamond as described by the carat with log 10 applied
```{r}
ggplot(jems2, aes(x= carat_log10, y=price_log10)) + 
  geom_point() +
  geom_smooth(method = "lm")
```


### Boxplots showing prices by color
```{r}
ggplot(jems2, aes(x = color, y = price))+
   geom_boxplot()

```

